Capitalized Title Here

### 2021-02-18 CMPSpaper_writing/CMPSpaper_writing.Rmd
adding references

---
title: Capitalized Title Here
header-includes:
  - \usepackage{xcolor}
author:
  # see ?rjournal_article for more information
  - name: Author One
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    url: https://journal.r-project.org
    orcid: 0000-0002-9079-593X
    email:  author1@work
  - name: Author Two
    url: https://journal.r-project.org
    email: author2@work
    orcid: 0000-0002-9079-593X
    affiliation: Affiliation 1
    address:
    - line 1 affiliation 1
    - line 2 affiliation 1
    affiliation2: Affiliation 2
    address2:
    - line 1 affiliation 2
    - line 2 affiliation 2
  - name: Author Three
    url: https://journal.r-project.org
    email: author3@work
    affiliation: Affiliation
    address:
    - line 1 affiliation
    - line 2 affiliation
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble

@@

An important task of firearm examination is \hh{to answer the question of whether wo pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm. Here, in particular, we are interested } to determine whether two bullets were fired from the same gun barrel. 
\hh{Assessing the similarity between two bullets is based on a comparison of  striation marks acquired during the firing process as bullets are propelled through the barrel. }

It is achievable because lands in a gun barrel create striation marks on the bullet during the firing process, and it is believed that the same gun barrel will create highly similar striation marks on the bullets it fired. Typically the striation marks are created by lands in a barrel, so the striation marks are also sometimes refered as land engravings, and the areas the marks occupy are called land engraved areas (LEA). Firearm examination has been playing an important role in terms of convictions in the United States criminal justice system. However, in recent years people became more cautious about firearms identification, and criticism of its subjective methodology arose. A report published by the National Academy of Sciences in 2009 states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those critics and concerns, people have been making an effort to build databases and develop frameworks and algorithms that can bring an objective and quantitative assessment into the field. The bullet signatures extracted from the bullet are important in this process since they can well describe the striation marks on the bullet and can well be understood by algorithms.

@@

The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [@brundage; @hamby; @Hamby:2019], and in particular, they are Hamby set 252 and Hamby set 44. For each Hamby set in the study, 35 bullets are fired by ten Ruger P-85 pistol barrels. 20 of the 35 bullets are known test bullets and 15 of them are unknown bullets. Each bullet has six land engraved areas (LEA) or land impressions, whose 3D topographical images were obtained and stored in the x3p format (XML 3-D Surface Profile). The x3p format provides a standard way of exchanging 2D and 3D profile data. It conforms to the ISO5436-2 standard [http://sourceforge.net/p/open-gps/mwiki/X3p/] and was adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science. Hamby set 252 were scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel. Hamby set 44 were scanned ...[at CSAFE?]... Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project.

>>>>

---
title: Capitalized Title Here
header-includes:
  - \usepackage{xcolor}
author:
  # see ?rjournal_article for more information
  - name: Author One
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    url: https://journal.r-project.org
    orcid: 0000-0002-9079-593X
    email:  author1@work
  - name: Author Two
    url: https://journal.r-project.org
    email: author2@work
    orcid: 0000-0002-9079-593X
    affiliation: Affiliation 1
    address:
    - line 1 affiliation 1
    - line 2 affiliation 1
    affiliation2: Affiliation 2
    address2:
    - line 1 affiliation 2
    - line 2 affiliation 2
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble

@@

 Firearm examination has been playing an important role in terms of convictions in the United States criminal justice system.

An important task of firearm examination is \hh{to answer the question of whether wo pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm. Here, in particular, we are interested } to determine whether two bullets were fired from the same gun barrel. 
\hh{Assessing the similarity between two bullets is based on a comparison of  striation marks acquired during the firing process as bullets are propelled through the barrel. }
\hh{Current state of art sees firearms examiners make an assessment of similarity based on a visual comparison, generally, using a comparison microscope. This practice has been criticized for its lack of objectivity and the associated problem in calculating an error rate [@pcast].}
<!--It is achievable because lands in a gun barrel create striation marks on the bullet during the firing process, and it is believed that the same gun barrel will create highly similar striation marks on the bullets it fired. Typically the striation marks are created by lands in a barrel, so the striation marks are also sometimes refered as land engravings, and the areas the marks occupy are called land engraved areas (LEA). However, in recent years people became more cautious about firearms identification, and criticism of its subjective methodology arose.--> A report published by @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those critics and concerns, reseaerchers have been making an effort to build databases [@nistdb] and develop frameworks and algorithms that can bring an objective and quantitative assessment into the field. The bullet signatures extracted from the bullet are important in this process since they can well describe the striation marks on the bullet and can well be understood by algorithms.

@@

The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [@brundage; @hamby; @Hamby:2019], and in particular, they are Hamby set 252 and Hamby set 44. For each Hamby set in the study, 35 bullets are fired by ten Ruger P-85 pistol barrels. 20 of the 35 bullets are known test bullets and 15 of them are unknown bullets. Each bullet has six land engraved areas (LEA) or land impressions, whose 3D topographical images were obtained and stored in the x3p format (XML 3-D Surface Profile). The x3p format provides a standard way of exchanging 2D and 3D profile data. It conforms to the ISO5436-2 standard [http://sourceforge.net/p/open-gps/mwiki/X3p/] and was adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science. Hamby set 252 were scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel. Hamby set 44 was scanned \hh{at the Roy J Carver High-Resolution microscopy lab at Iowa State. These scans were acquired with a Sensofar Confocal Light Microscope at 20x magnification for a nominal resolution of 0.645 \textmu m $\times$ 0.645 \textmu per pixel}.  Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project [@nistdb].
